Derogations and Democratic Backsliding: Exploring the Pandemic's Effects on Civic Spaces

### 2021-03-19 analysis/index.Rmd
Clean and process data

---
title: "Derogations and Democratic Backsliding: Exploring the Pandemic's Effects on Civic Spaces"
author: "Suparna Chaudhry and Andrew Heiss"
date: "`r format(Sys.time(), '%F')`"
# site: safesite::safesite
---

>>>>

---
title: "Derogations and Democratic Backsliding: Exploring the Pandemic's Effects on Civic Spaces"
author: "Suparna Chaudhry and Andrew Heiss"
date: "`r format(Sys.time(), '%F')`"
---
